---
title: "Social Science - CDC 2024"
author: "Sean Shen, Jabbir Ahmed, Abrar Ahmed"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE, warning=F}
library(tidyverse)
library(nortest)
library(cluster)
library(factoextra)
library(readxl)

travel_df <- read_csv("Social_Science_Dataset.csv")
```


```{r, include=F}
#data cleaning
head(travel_df)
names(travel_df)

category <- c("Unique user id",
"churches",
"resorts",
"beaches", 
"parks", 
"theatres", 
"museums", 
"malls", 
"zoo", 
"restaurants", 
"pubs/bars", 
"local services",
"burger/pizza shops", 
"hotels/other lodgings", 
"juice bars", 
"art galleries", 
"dance clubs", 
"swimming pools", 
"gyms", 
"bakeries",
"beauty & spas", 
"cafes",
"view points",
"monuments",
"gardens")

travel_df=travel_df[-1, -26]

#rename columns
for (i in 1:ncol(travel_df)){
  names(travel_df)[i]=category[i]
}

#remove "User " from `Unique user id`
for (i in 1:nrow(travel_df)){
  travel_df$`Unique user id` = 
    str_replace(travel_df$`Unique user id`, "User ", "")
}


#convert numbers from character to double
for (i in 2:ncol(travel_df)){
  travel_df[[i]]=as.numeric(travel_df[[i]])
}

names(travel_df)
head(travel_df)

```

```{r}
#cleaned data
head(travel_df)
```


```{r}
#check normality using Anderson-Darling Test
normality_by_category <- data.frame(category=c(rep(-1, 24)),
                                   A=c(rep(-1, 24)), 
                                      `p-value`=c(rep(-1, 24)))
A=c(rep(-1, 24))
p=c(rep(-1, 24))

normality_by_category$category=names(travel_df)[-1]

for (i in 2:25){
  temp <- travel_df[[i]][travel_df[[i]]!=0]
  
  A[i-1]=ad.test(temp)[1]
  p[i-1]=ad.test(temp)[2]
}
normality_by_category$A=unlist(A)
normality_by_category$`p-value`=unlist(p)

normality_by_category$normality=ifelse(normality_by_category$`p-value`>=0.05, 
                                       1, 0)

normality_by_category<- normality_by_category[, -3]
normality_by_category
```

```{r}
#histograms to see distributions of all the categories
for (i in 2:25){
  temp <- travel_df[[i]][travel_df[[i]]!=0]
  hist(temp, main=names(travel_df)[i])
}
```



```{r}
set.seed(123)
travel_kms <- na.omit(travel_df[, -1])

sil <- c(rep(-2, 9))

#k=2 to k=10
for (k in 2:10){
  kmeans_out <- kmeans(travel_kms, centers = k, nstart=25)
  sil_score<- silhouette(kmeans_out$cluster, dist(travel_kms))
  sil[k-1]<- summary(sil_score)$avg.width
}
## Credit to Chat gpt

best_k <-which.max(sil)+1 #k=9 gives the highest silhouette value

kmeans_result <- kmeans(travel_kms, centers = best_k, nstart = 25)
# Preview the first few rows to check for extra rows
head(travel_df)

# Assuming the last two rows are extra and should be removed
# Remove the last two rows
travel_df_clean <- travel_df[-c((nrow(travel_df)-1):nrow(travel_df)), ]

# Alternatively, if the extra rows are at the beginning or somewhere else, you can manually inspect them and decide:
# travel_df_clean <- travel_df[-c(row_indices_to_remove), ]

# Now rename the columns using the provided category names
colnames(travel_df_clean) <- c("Unique_user_id",
                               "churches", "resorts", "beaches",
                               "parks", "theatres", "museums",
                               "malls", "zoo", "restaurants",
                               "pubs_bars", "local_services",
                               "burger_pizza_shops",
                               "hotels_other_lodgings",
                               "juice_bars", "art_galleries",
                               "dance_clubs", "swimming_pools",
                               "gyms", "bakeries", "beauty_spas",
                               "cafes", "view_points",
                               "monuments", "gardens")

# Check the cleaned dataset
head(travel_df_clean)

# Add the cluster labels to the dataset
travel_df_clean$cluster <- kmeans_result$cluster
travel_df_clean$cluster <- kmeans_result$cluster
## Credit to Chat gpt

kmeans.out <- kmeans(travel_kms, centers = 9, nstart=25)
```






-------------------------------------------------------- Jabbir 
```{r}

# Load necessary libraries
library(dplyr)
library(randomForest)

# Assuming your data has clusters assigned
# Splitting data into training (70%) and testing (30%) sets
set.seed(123)
train_indices <- sample(1:nrow(travel_df_clean), 0.7 * nrow(travel_df_clean))
train_data <- travel_df_clean[train_indices, ]
test_data <- travel_df_clean[-train_indices, ]


# Train a Random Forest model
rf_model <- randomForest(cluster ~ ., data = train_data[-1], ntree = 100)

# Print model summary
print(rf_model)

# Predict on the test set
predictions <- predict(rf_model, test_data[-1])

# Create confusion matrix to evaluate performance
confusion_matrix <- table(test_data$cluster, predictions)
print(confusion_matrix)

# Plot feature importance
importance(rf_model)
varImpPlot(rf_model)

```
```{r}
# Bar plot for IncNodePurity
importance_df <- data.frame(
  category = rownames(importance(rf_model)),
  importance = importance(rf_model)[, "IncNodePurity"]
)

library(ggplot2)

ggplot(importance_df, aes(x = reorder(category, importance), y = importance)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  labs(title = "Feature Importance (IncNodePurity) from Random Forest Model",
       x = "Attraction Type",
       y = "IncNodePurity") +
  theme_minimal()

```

```{r}
# Sample DataFrame (replace this with your actual data)
travel_df_clean <- data.frame(
  category = c("churches", "resorts", "beaches", "parks", "theatres", "museums", 
               "malls", "zoo", "restaurants", "pubs_bars", "local_services", 
               "burger_pizza_shops", "hotels_other_lodgings", "juice_bars", 
               "art_galleries", "dance_clubs", "swimming_pools", "gyms", 
               "bakeries", "beauty_spas", "cafes", "view_points", "monuments", "gardens"),
  average_rating = runif(24, 1, 5), # Random ratings between 1 and 5
  visitor_numbers = sample(100:1000, 24, replace = TRUE) # Random visitor numbers
)

# Add a cluster variable based on importance (for demonstration)
importance_threshold <- median(c(381.6302, 530.1468, 1929.6702, 5334.6368, 4304.3620, 
                                  516.2777, 297.1897, 3032.7217, 1934.8890, 2507.0687, 
                                  1041.5066, 590.2555, 485.8014, 953.0920, 985.3714, 
                                  322.5823, 309.0884, 431.7453, 484.9232, 265.4240, 
                                  224.7806, 474.6157, 481.0322, 974.8897))

travel_df_clean$importance_group <- ifelse(travel_df_clean$category %in% 
                                              c("parks", "beaches", "zoo", "restaurants", "pubs_bars"), 
                                            "Highly Important", "Less Important")
# Load necessary library
library(dplyr)

# Summarize data
summary_df <- travel_df_clean %>%
  group_by(importance_group) %>%
  summarize(
    avg_rating = mean(average_rating),
    total_visitors = sum(visitor_numbers),
    num_categories = n()
  )

print(summary_df)
# Load visualization library
library(ggplot2)

# Bar plot for average ratings
ggplot(summary_df, aes(x = importance_group, y = avg_rating, fill = importance_group)) +
  geom_bar(stat = "identity") +
  labs(title = "Average Ratings by Importance Group",
       x = "Importance Group",
       y = "Average Rating") +
  theme_minimal() +
  scale_fill_manual(values = c("Highly Important" = "lightblue", "Less Important" = "lightcoral"))
# Bar plot for total visitors
ggplot(summary_df, aes(x = importance_group, y = total_visitors, fill = importance_group)) +
  geom_bar(stat = "identity") +
  labs(title = "Total Visitor Numbers by Importance Group",
       x = "Importance Group",
       y = "Total Visitors") +
  theme_minimal() +
  scale_fill_manual(values = c("Highly Important" = "blue", "Less Important" = "red"))



# Sample testimonials (replace this with your actual data)
testimonials <- data.frame(
  category = c("parks", "beaches", "theatres"),
  testimonial = c("I love the open spaces and nature trails!", 
                  "The beach was beautiful and relaxing.", 
                  "Great performances and cultural experience.")
)
## Credit to Chat gpt

# Print testimonials
print(testimonials)


# Sample testimonials for less important categories
testimonials_less_important <- data.frame(
  category = c("bakeries"),
  testimonial = c("I visited a local bakery while exploring the city. It had a nice atmosphere, but it was just an average experience compared to other attractions.")
)
## Credit to Chat gpt

# Print testimonials for less important category
print(testimonials_less_important)
## Credit to Chat gpt


```
The above code prepares your data, calculates averages, and visualizes the importance of different attraction categories based on user ratings and visitor numbers.

improve the project by including real testimonials from users to enrich the narrative.

This information will help illustrate how different types of attractions can influence visitor decisions in Europe.



```{r}
# Load necessary libraries
library(dplyr)
library(ggplot2)

# Sample data of attraction categories and their attributes for nightlife thrill seekers
attraction_data <- data.frame(
  category = c("dance clubs", "swimming pools", "spas", "cafes"),
  attributes = I(list(
    c("nightlife", "music", "dancing"),  # Dance clubs
    c("nightlife", "relaxation", "fun"), # Swimming pools
    c("relaxation", "wellness", "luxury"), # Spas
    c("socializing", "casual", "food")    # Cafes
  )),
  # Updated importance scores
  importance_score = c(4.510389, 4.367149, 2.70572, 3.340826) 
)

# Function to get user input for preferences
get_user_preferences <- function() {
  cat("What do you enjoy? (Select all that apply, comma-separated)\n")
  cat("1. Nightlife\n")
  cat("2. Relaxation\n")
  cat("3. Socializing\n")
  
  # Simulated user input for nightlife thrill seeker
  user_input <- "nightlife,relaxation" # Replace this with real user input in practice
  return(unlist(strsplit(user_input, ",")))
}

# Function to filter recommendations based on user preferences
get_recommendations <- function(user_preferences, data) {
  relevant_categories <- data %>%
    filter(sapply(attributes, function(attr) any(attr %in% user_preferences)))

  return(relevant_categories)
}

# Function to display importance of recommended categories
display_importance <- function(recommendations) {
  cat("\nRecommended Attractions:\n")
  print(recommendations %>% select(category, importance_score))
}

# Main flow
user_preferences <- get_user_preferences()
recommendations <- get_recommendations(user_preferences, attraction_data)

# Prioritize recommendations: Dance clubs, Swimming pools, and Spas over Cafes
recommended_categories <- recommendations %>%
  filter(category %in% c("dance clubs", "swimming pools", "spas")) %>%
  arrange(desc(importance_score))

# Display recommendations
display_importance(recommended_categories)

# Visualization
ggplot(recommended_categories, aes(x = reorder(category, importance_score), y = importance_score, fill = category)) +
  geom_bar(stat = "identity") +
  coord_flip() + # Flip coordinates for better visibility
  labs(title = "Importance of Recommended Attractions for Nightlife Thrill Seekers",
       x = "Attraction Categories",
       y = "Importance Score") +
  theme_minimal() +
  theme(legend.position = "none") # Remove legend for simplicity




## Credit to Chat gpt
```

